\documentclass[11pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,calc,decorations.pathreplacing,fit,backgrounds}
\geometry{margin=1in}

% Code listing styles
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\color{green!60!black},
    stringstyle=\color{red},
    numbers=left,
    numberstyle=\tiny\color{gray},
    frame=single,
    breaklines=true,
    breakatwhitespace=true,
    tabsize=2,
    showspaces=false,
    showstringspaces=false
}

% MQL5 listing style
\lstdefinestyle{mql5}{
    language=C,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\color{green!60!black},
    stringstyle=\color{red},
    numbers=left,
    numberstyle=\tiny\color{gray},
    frame=single,
    breaklines=true
}

% OCaml listing style
\lstdefinestyle{ocaml}{
    language=ML,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    commentstyle=\color{green!60!black},
    stringstyle=\color{red},
    numbers=left,
    numberstyle=\tiny\color{gray},
    frame=single,
    breaklines=true,
    showstringspaces=false
}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE]{\leftmark}
\fancyhead[RO]{\rightmark}
\fancyfoot[C]{\thepage}

\title{From Generation One to Generation Two:\\
Evolution of Quantum-Enhanced Alpha Mining Systems\\
A Complete Guide to Building Self-Optimizing Trading Strategy Discovery Platforms\\
\& Operating a One-Man Quant Trading Firm}
\author{zhutoutoutousan}
\date{\today}

\begin{document}

\frontmatter

\maketitle

\begin{abstract}
This comprehensive book documents the evolution from Generation One to Generation Two alpha mining systems. It provides a complete architectural guide to the \texttt{consultant-templates-ollama} system, including detailed code analysis, module descriptions, and implementation patterns. The book then extends to Generation Two with self-optimization capabilities, genetic algorithm-based evolution, continuous mining with automated error correction, template validation with self-correcting AST, expression compilation pipeline, and a modern cyberpunk GUI interface. Generation Two features modular architecture, smart Ollama integration with automatic fallback, concurrent simulation execution, quality monitoring, and 24/7 continuous alpha discovery. Additionally, it incorporates MetaTrader 5 expert advisor development experience and presents a complete Mini-Quant system—a self-sustained full-lifecycle quantitative research platform optimized for one-man operations. The book includes a comprehensive guide to operating a one-man quant trading firm, covering public data sources, multi-region backtesting (EMEA, AMER, IND, CHN, USA), alpha management, trade execution, AI decision-based hedging, and unique price action trading strategies combining data simplicity with MT5 operational depth.
\end{abstract}

\tableofcontents
\listoffigures
\listoftables

\mainmatter

% Part I: Generation One Architecture
\part{Generation One: Foundation Architecture}

\input{chapters/generation-one-architecture}

% Part II: Generation Two Evolution
\part{Generation Two: Self-Optimization and Evolution}

\input{chapters/generation-two-improvements}

\chapter{Continuous Mining and Error Correction}
This chapter covers the continuous mining system with automated template generation, simulation submission, error detection, and self-correcting template validation. The system features infinite retry mechanisms for critical errors, field placeholder replacement, and real-time progress monitoring.

\chapter{Template Validation and Expression Compilation}
This chapter details the multi-stage expression compilation pipeline, self-correcting AST system, error learning mechanisms, and prompt engineering for template fixes. The system learns from simulation errors and applies corrections automatically.

\chapter{GUI and User Interface}
This chapter describes the cyberpunk-themed GUI interface, workflow panels, continuous mining controls, and real-time monitoring capabilities. The modular GUI architecture separates concerns for maintainability.

% Part III: Advanced Technologies
\part{Advanced Technologies and Integration}

\input{chapters/quantum-computing-integration}

\input{chapters/mt5-expert-advisor-experience}

\input{chapters/fast-depth-hybrid-expressions}

% Part IV: Mini-Quant System
\part{Mini-Quant: One-Man Quant Trading Firm}

\input{chapters/one-man-quant-trading-firm}

% Part V: Execution Systems
\part{Execution Systems: From Backtesting to Market Actions}

\input{chapters/ocaml-backtesting-execution}

% Part VI: Cryptocurrency Trading
\part{Cryptocurrency Trading: Advanced Strategies and Broker Integration}

\input{chapters/crypto-trading-strategies}

% Part VII: Commercial Models and Gaming Platforms
\part{Commercial Models and Gaming Platforms}

\input{chapters/b2b-alpha-signals}
\input{chapters/b2c-trading-platform}
\input{chapters/gaming-trading-platform}

\appendix

\chapter{API Reference}

\section{WorldQuant Brain API}
Complete API reference for alpha simulation and evaluation.

\section{MT5 API}
MetaTrader 5 API documentation for broker integration.

\chapter{Code Examples}

\section{Generation One Complete Examples}
Full working examples from the consultant-templates-ollama system.

\section{Generation Two Implementation Examples}
Self-optimization and genetic algorithm implementations.

\backmatter

\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{99}

\bibitem{worldquant2015}
WorldQuant Brain, ``Alpha Mining Platform,'' \textit{WorldQuant}, 2015.

\bibitem{farhi2014}
E. Farhi, J. Goldstone, and S. Gutmann, ``A Quantum Approximate Optimization Algorithm,'' \textit{arXiv preprint arXiv:1411.4028}, 2014.

\bibitem{peruzzo2014}
A. Peruzzo et al., ``A variational eigenvalue solver on a photonic quantum processor,'' \textit{Nature Communications}, vol. 5, p. 4213, 2014.

\bibitem{mt5docs}
MetaQuotes Software Corp., ``MQL5 Reference,'' \textit{https://www.mql5.com/en/docs}, 2024.

\bibitem{holland1992}
J. H. Holland, \textit{Adaptation in Natural and Artificial Systems}. MIT Press, 1992.

\bibitem{deb2002}
K. Deb et al., ``A fast and elitist multiobjective genetic algorithm: NSGA-II,'' \textit{IEEE Transactions on Evolutionary Computation}, vol. 6, no. 2, pp. 182-197, 2002.

\bibitem{gradzki2025}
P. Grądzki, P. Wójcik, and S. Lessmann, ``Algorithmic crypto trading using information-driven bars, triple barrier labeling and deep learning,'' \textit{Financial Innovation}, vol. 11, article 136, 2025. \url{https://doi.org/10.1186/s40854-025-00866-w}

\end{thebibliography}

\end{document}

